Supplementary Information: Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient

### 2019-10-20 paper/cvpr2020/sections/discussion.tex
Updated figures, shortened back to 8 pages.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Limitations}
The performance of our method is highly dependent on the accuracy of the initial depth map output by the monocular depth estimation algorithm.
%Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
Our results demonstrate that when the MDE technique produces a depth map
with good ordinal depth, where the ordering object depth is roughly correct, the
depth estimate can be corrected to produce accurate absolute depth. However, if the ordinal depth of the initial estimate is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.

Additionally, since our method relies on a diffused pulsed laser, the laser
power is spread out over the entire scene. Accordingly for distant scene points very
little light will return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited to short to medium-range scenes.

@@

Other methods for extracting scene information from the SPAD histogram could be
also employed, including learning-based methods to combine the MDE and
histogram. One might even consider sensing regimes where the number of
returning signal photons is low, such as when the SPAD and camera operate
at high framerates. While most MDE techniques are tailored to clean RGB images,  
the SPAD histogram could be used to help MDE
techniques generalize to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, the performance of monocular depth estimation algorithms has improved tremendously.  However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements. 
This suggests we are approaching the limits of what can be achieved using a monocular image alone. 
In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histograms measurements. 
Such histograms are easy to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Limitations}
The performance of our method is highly dependent on the accuracy of the initial
depth map of the MDE algorithm.
%Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
Our results demonstrate that when the MDE technique produces a depth map
with good ordinal accuracy, where the ordering of object depths is roughly correct, the
depth estimate can be corrected to produce accurate absolute depth. However, if
the ordering of the initial depths is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.

Additionally, since our method relies on a diffused pulsed laser, the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light will return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited to short to medium-range scenes.

@@

Other methods for extracting scene information from the SPAD histogram could be
employed, including learning-based methods to combine the MDE and
histogram. One might even consider sensing regimes where the number of
returning signal photons is low, such as when the SPAD and camera operate
at high framerates. While most MDE techniques are tailored to clean RGB images,  
the SPAD histogram could be used to help MDE
techniques generalize to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Since their introduction, monocular depth estimation algorithms have improved tremendously.  However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements. 
In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histogram measurements. 
Such histograms are easy to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.

### 2019-10-20 paper/cvpr2020/sections/hardware.tex
Updated figures, shortened back to 8 pages.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left). A monocular depth CNN predicts an initial depth map (top middle), which is corrected with the diffused SPAD histogram using the proposed method (top right). As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right). The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print. Our method is able to correct this error. }
	\label{fig:results_captured}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth
    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
    image (lower left). A monocular depth CNN predicts an initial depth map (top
    middle), which is corrected with the diffused SPAD histogram using the
    proposed method (top right), as shown by the error maps and root mean
    squared error (RMSE) for each example (lower center, right). The CNN is
    confused when we show it a photograph of a poster (bottom scene); it
    incorrectly predicts the depth of the scene depicted on the flat print. Our
    method is able to correct this error.}
	\label{fig:results_captured}
\end{figure}
